Variant calling with transformers

### 2022-03-04 manuscript/manuscript.tex

@@

@@

@@

@@

 \vspace{8pt}
 \subsection{Ablation experiments}
Vaswani, Ashish, et al. "Attention is all you need." Advances in neural information processing systems 30 (2017).

>>>>

Recent years have seen the transformer architecture, originally designed for language modelling, expand to multiple new areas, including vision (Dosovitskiy et al. 2020, Liu et al. 2021), video (Arnab et al. 2021), and others. To our knowledge this is the first use of transformers for use of haplotype construction or variant detection in next generation sequencing data.

Modern variant detection tools are extremely accurate, and generally result in very high sensitivity and specificity.

 In his essay "The Bitter Lesson" Richard Sutton remarked that "methods that leverage general computation" often outperform methods with handcrafted statistical or heuristic techniques.  Our work continues in this tradition, replacing the myriad finely tuned algorithms with a single model, learned end-to-end.

@@

 \vspace{8pt}
 Arnab, Anurag, et al. "Vivit: A video vision transformer." Proceedings of the IEEE/CVF International Conference on Computer Vision. 2021.

@@

\vspace{8pt}
Dosovitskiy, Alexey, et al. "An image is worth 16x16 words: Transformers for image recognition at scale." arXiv preprint arXiv:2010.11929 (2020).

@@

\vspace{8pt}
Liu, Ze, et al. "Swin transformer: Hierarchical vision transformer using shifted windows." Proceedings of the IEEE/CVF International Conference on Computer Vision. 2021.

@@

\vspace{8pt}
Vaswani, Ashish, et al. "Attention is all you need." Advances in neural information processing systems 30 (2017).
